MS_CNuptake.Rmd

### 2022-10-23 MS_CNuptake.Rmd
tiny update

(some metric info such as number of sites and species was shown as 'metric_info', that will be inputted in Method text)
(metric info was primarily using individual numbers in Fig.1 - validation figure)

>>>>

(some metric info such as number of sites and species was shown as 'metric_info', that will be inputted in Method text)
(metric info was primarily using individual numbers in Fig.2 - validation figure)
